### 2015-03-24 swmpr_manu.Rnw
processed all new cdmo data for metabolism, added plot

A second approach for importing \ac{SWMP} data into R is using the \texttt{import\_remote} function.  This method imports site data into R from an independent server where \ac{SWMP} data have been downloaded previously and uploaded as \texttt{swmpr} objects in .RData binary format.  This approach is advantageous because the files can be imported very quickly and the computer's IP address does not need to be registered.  The files are hosted via third party web services and include almost all available \ac{SWMP} data for each site up to December 2014.  Always use the \ac{CDMO} for the most recent data.  The files can be accessed by copying the URL to a web browser (see the \Cref{sec:supp_info}) or by using the function as follows.

@@

Example data as raw, comma-separated files have not been included in the package due to size limitations.  However, a sample dataset can be \href{https://s3.amazonaws.com/swmpexdata/zip_ex.zip}{downloaded} for use with the examples below.  This dataset has an identical format as the data returned from the zip downloads feature of the \ac{CDMO}.  Processed verions of the raw data are included with the package as binary data files (.RData) to decrease processing times with the examples.  Information for each binary file can be viewed as follows.

@@

Estimates of ecosystem metabolism provide a useful measure of overall system productivity.  These estimates are commonly used to evaluate whether an ecosystem is a net source or sink of organic material.  The open-water method \cite{Odum56} is a common approach to quantify net ecosystem metabolism using a mass balance equation that describes the change in dissolved oxygen over time from the balance between photosynthetic and respiration processes, corrected using an empirically constrained air-sea gas diffusion model (see Ro and Hunt \cite{Ro06}, Thebault et al. \cite{Thebault08}). The diffusion-corrected \ac{DO} flux estimates are averaged separately over each day and night of the time series. The nighttime average \ac{DO} flux is used to estimate respiration rates, while the daytime \ac{DO} flux is used to estimate net primary production. To generate daily integrated rates, respiration rates are assumed constant such that hourly night time \ac{DO} flux rates are multiplied by 24. Similarly, the daytime \ac{DO} flux rates are multiplied by the number of daylight hours, which varies with location and time of year, to yield net daytime primary production. Respiration rates are subtracted from daily net production estimates to yield gross production rates. The metabolic day is considered the 24 hour period between sunsets on two adjacent calendar days

The \texttt{ecometab} function is used to implement an adaptation of the open-water method \cite{Odum56,Caffrey14}.  Several assumptions must be met for a valid interpretation of the results.  In general, the dissolved oxygen time series is assumed to represent the same water mass over time.  Tidal advection may have a significant influence on the time series, which can contribute to a significant amount of noise in metabolic estimates.  The extent to which tidal advection influences the dissolved oxygen signal depends on various site-level characteristics and an intimate knowledge of the site may be required.  Areal rates for gross production and total respiration are based on volumetric rates normalized to the depth of the water column at the sampling location, which is assumed to be well-mixed, such that the water quality sensor is reflecting the integrated processes in the entire water column (including the benthos).  Water column depth is calculated as the mean value of the depth variable across the time series in the \texttt{swmpr} object. Depth values are floored at one meter for very shallow stations and 0.5 meters is also added to reflect the practice of placing sensors slightly off of the bottom.  Additionally, the air-sea gas exchange model is calibrated with wind data either collected at, or adjusted to, wind speed at 10 m above the surface.  The metadata should be consulted for exact height. Other assumptions may apply and the user should consult the relevant literature.  All calculations within the function are done using molar units (e.g., mmol O$^2$ m$^{-3}$). The output can be returned as mass units by changing the default argument. Input data must be in standard mass units for \ac{DO} (mg L-1)

@@

First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at the \ac{NERRS} reserve for all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update to results described in Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04}.   The results are presented to facilitate additional research to evaluate factors that influence variation between sites.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} describe the theory and application of the open-water method to estimate ecosystem metabolism using two sites at each of the \ac{NERRS} reserve.  Time series data included approximately five years of half-hour water quality observations at each site.  Additionally, the air-sea gas exchange model, as implemented by the current \texttt{ecometab} function (see Ro and Hunt \cite{Ro06} and Thebault et al. \cite{Thebault08}), was not incorporated into the initial metabolism estimates such that a constant value for the reaeration coefficient was assumed.  This coefficient provides an estimate of the rate of air-sea gas exchange that varies as a function of wind speed, temperature, barometric pressure, salinity, and depth of the water column  The inclusion of weather data in the calculation allows for a more precise estimate of air-sea gas exchange and consequently more reliable estimates of ecosystem metabolism (see Caffrey et al. \cite{Caffrey14} for details).

All water quality and weather observations for all \ac{NERRS} sites were obtained through a bulk data request in November 2014 using the \href{http://cdmo.baruch.sc.edu/aqs/zips.cfm}{zip downloads} feature of \ac{CDMO}.  After the download was complete, all csv files for each station were imported into R using the \texttt{import\_local} function, saved again on a local hard drive as a binary .RData file, and uploaded.  This resulted in a single \texttt{swmpr} object for each site.  All files were then uploaded to a remote server.  An \href{https://gist.github.com/fawda123/4fc51c2cb86341ed9291}{R script} was executed that retrieved and processed combined water quality and weather data for each site.

<<eval = F, echo = F>>=
# # packages to use
# library(SWMPr)
# library(httr)
# library(XML)
# library(foreach)
# library(doParallel)
# 
# # names of files on server
# files_s3 <- httr::GET('https://s3.amazonaws.com/swmpalldata/')$content
# files_s3 <- rawToChar(files_s3)
# files_s3 <- htmlTreeParse(files_s3, useInternalNodes = T)
# files_s3 <- xpathSApply(files_s3, '//contents//key', xmlValue)
# files_s3 <- gsub('\\.RData$', '', files_s3) 
# 
# # find only active water quality and weather sites
# # IP address must be registed with CDMO 
# meta <- site_codes()
# sel <- meta$status %in% 'Active' & !grepl('nut$', meta$station_code)
# meta <- meta[sel, ]
# 
# # get wq sites from meta, then filter by those on server
# wq_sites <- grep('wq$', meta$station_code, value = T)
# wq_sites <- files_s3[gsub('\\.RData$', '', files_s3) %in% wq_sites]
# 
# ##
# # process each site
# 
# # setup parallel backend for processing
# cl <- makeCluster(8)
# registerDoParallel(cl)
# strt <- Sys.time()
# 
# # output
# metabs <- foreach(wq_site = wq_sites) %dopar% {
#  
#   library(SWMPr)
#   
#   # progress
#   sink('log.txt')
#   cat(wq_site, which(wq_site == wq_sites), 'of', length(wq_sites), '\n')
#   print(Sys.time() - strt)
#   sink()
#   
#   # find corresponding wx station
#   met_site <- substr(wq_site, 1, 3)
#   met_site <- grep(paste0('^', met_site, '.*met'), files_s3, value = T)
#   met_site <- gsub('\\.RData$', '', met_site)
#   
#   # continue if wx data found
#   if(length(met_site) > 0){
#   
#     ##
#     # load the files
#     
#     # wq
#     wq <- import_remote(wq_site)
#     
#     # met
#     met <- import_remote(met_site)
#     
#     ## 
#     # combine, subset up to 2013, estimate metabolism, reduce data volume
#     dat <- comb(wq, met, method = met_site)
#     dat <- subset(dat, subset = '2014-01-01 0:0', operator = '<')
#     dat <- ecometab(dat)
#     dat <- dat[1, ]
#     
#     dat
#     
#   }
#   
# }
# names(metabs) <- wq_sites
# save(metabs, file = 'metabs.RData')

# make a plot.....

@@

% add figs to show each....

@@

Quickly access all \ac{SWMP} data: \href{https://s3.amazonaws.com/swmpalldata/}{https://s3.amazonaws.com/swmpalldata/}

This is an online link for all \ac{SWMP} data from January 1994 to December 2014 as binary .RData files.  Separate files are available for each site and parameter type, e.g., acebbnut.RData includes all available nutrient data for the Big Bay site at ACE Basin.  Individual files can be downloaded by pasting the file name to the URL, e.g., \href{https://s3.amazonaws.com/swmpalldata/acebbnut.RData}{https://s3.amazonaws.com/swmpalldata/acebbnut.RData}, then using the \texttt{load} function to import the file in the current R workspace.  Files can also be downloaded directly within R using \texttt{import\_remote} function.

>>>>

A second approach for importing \ac{SWMP} data into R is using the \texttt{import\_remote} function.  This method imports site data into R from an independent server where \ac{SWMP} data have been downloaded previously and uploaded as \texttt{swmpr} objects in RData binary format.  This approach is advantageous because the files can be imported very quickly and the computer's IP address does not need to be registered.  The files are hosted via third party web services and include almost all available \ac{SWMP} data for each site up to December 2014.  Always use the \ac{CDMO} for the most recent data.  The files can be accessed by copying the URL to a web browser with the site name and file extension (e.g., \href{https://s3.amazonaws.com/swmpalldata/acebbnut.RData}{https://s3.amazonaws.com/swmpalldata/acebbnut.RData}, see the \nameref{supp_info}) or by using the function as follows.

@@

Example data as raw, comma-separated files have not been included in the package due to size limitations.  However, a sample dataset can be \href{https://s3.amazonaws.com/swmpexdata/zip_ex.zip}{downloaded} for use with the examples below.  This dataset has an identical format as the data returned from the zip downloads feature of the \ac{CDMO}.  Processed verions of the raw data are included with the package as binary data files (RData) to decrease processing times with the examples.  Information for each binary file can be viewed as follows.

@@

Estimates of ecosystem metabolism provide a measure of overall system productivity to evaluate whether an ecosystem is a net source or sink of organic material.  The open-water method \cite{Odum56} is a common approach to quantify metabolism using a mass balance equation that describes the change in dissolved oxygen over time from the balance between photosynthetic and respiration processes, corrected using an empirically constrained air-sea gas diffusion model (see Ro and Hunt \cite{Ro06}, Thebault et al. \cite{Thebault08}). The diffusion-corrected \ac{DO} flux estimates are averaged separately over each day and night of the time series. The nighttime average \ac{DO} flux is used to estimate respiration rates, while the daytime \ac{DO} flux is used to estimate net primary production. To generate daily integrated rates, respiration rates are assumed constant such that hourly night time \ac{DO} flux rates are multiplied by 24. Similarly, the daytime \ac{DO} flux rates are multiplied by the number of daylight hours, which varies with location and time of year, to yield net daytime primary production. Respiration rates are subtracted from daily net production estimates to yield gross production rates. The metabolic day is considered the 24 hour period between sunsets on two adjacent calendar days

The \texttt{ecometab} function is used to implement the open-water method with a combined water quality and weather dataset \cite{Caffrey14}.  Several assumptions must be met for a valid interpretation of the results.  In general, the dissolved oxygen time series is assumed to represent the same water mass over time.  Tidal advection may have a significant influence on the time series, which can contribute to a significant amount of noise in metabolic estimates.  The extent to which tidal advection influences the dissolved oxygen signal depends on various site-level characteristics and an intimate knowledge of the site may be required.  Areal rates for gross production and total respiration are based on volumetric rates normalized to the depth of the water column at the sampling location, which is assumed to be well-mixed, such that the water quality sensor is reflecting the integrated processes in the entire water column (including the benthos).  Water column depth is calculated as the mean value of the depth variable across the time series in the \texttt{swmpr} object. Depth values are floored at one meter for very shallow stations and 0.5 meters is also added to reflect the practice of placing sensors slightly off of the bottom.  Additionally, the air-sea gas exchange model is calibrated with wind data either collected at, or adjusted to, wind speed at 10 m above the surface.  The metadata should be consulted for exact height. Other assumptions may apply and relevant resources should be consulted to ensure appropriate application of the open-water method (see \cite{Kemp12,Needoba12}).

@@

First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at the \ac{NERRS} reserve for all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update to results described in Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} using the most recent \ac{SWMP} data.  Additionally, previous methods to evaluate metabolism at \ac{NERRS} reserves did not incorporate \textit{in situ} weather data to estimate the air-sea gas exchange model.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} applied the open-water method to estimate ecosystem metabolism using five years of water quality observations at two sites at each of the \ac{NERRS} reserves.  Additionally, the air-sea gas exchange model assumed a constant value for the reaeratio coefficientt.  This coefficient provides an estimate of the rate of air-sea gas exchange that varies as a function of wind speed, temperature, barometric pressure, salinity, and depth of the water column.  The inclusion of weather data in the calculation allows for a more precise estimate of air-sea gas exchange and consequently more reliable estimates of ecosystem metabolism (see Caffrey et al. \cite{Caffrey14} for details).

Water quality and weather observations from January 1995 to December 2014 for all \ac{NERRS} sites were obtained through a bulk data request using the \href{http://cdmo.baruch.sc.edu/aqs/zips.cfm}{zip downloads} feature of \ac{CDMO}.  After the download was complete, all csv files for each station were imported into R using the \texttt{import\_local} function, processed using the \texttt{setstep} and \texttt{qaqc} functions, then saved on a local hard drive as binary RData files (see \href{https://github.com/fawda123/swmp_rats/blob/master/R/dat_proc.R}{here} for the R script). This resulted in a single \texttt{swmpr} object for each paramter at each site.  All files were then uploaded to a remote server.  An \href{https://gist.github.com/fawda123/4fc51c2cb86341ed9291}{R script} was executed that retrieved and processed combined the water quality and weather data for each site.

<<metab_plo, eval = T, cache = T, echo = F, fig.cap = 'Aggregated estimates of net metabolism, gross production, and total respiration for two sites at each \\ac{NERRS} reserve.  Values are daily integrated estimates as mean annual values averaged across all years with 95\\% confidence intervals.  Two sites were chosen from each reserve that had the longest available time series.', fig.height = 6, fig.width = 8>>=
# # packages to use
# library(SWMPr)
# library(httr)
# library(XML)
# library(foreach)
# library(doParallel)
# 
# # names of files on server
# files_s3 <- httr::GET('https://s3.amazonaws.com/swmpalldata/')$content
# files_s3 <- rawToChar(files_s3)
# files_s3 <- htmlTreeParse(files_s3, useInternalNodes = T)
# files_s3 <- xpathSApply(files_s3, '//contents//key', xmlValue)
# files_s3 <- gsub('\\.RData$', '', files_s3) 
# 
# # find only active water quality and weather sites
# # IP address must be registed with CDMO 
# meta <- site_codes()
# sel <- meta$status %in% 'Active' & !grepl('nut$', meta$station_code)
# meta <- meta[sel, ]
# 
# # get wq sites from meta, then filter by those on server
# wq_sites <- grep('wq$', meta$station_code, value = T)
# wq_sites <- files_s3[gsub('\\.RData$', '', files_s3) %in% wq_sites]
# 
# # setup parallel backend for processing
# cl <- makeCluster(8)
# registerDoParallel(cl)
# strt <- Sys.time()
# 
# # process
# metabs <- foreach(wq_site = wq_sites) %dopar% {
#  
#   library(SWMPr)
#   
#   # progress
#   sink('log.txt')
#   cat(wq_site, which(wq_site == wq_sites), 'of', length(wq_sites), '\n')
#   print(Sys.time() - strt)
#   sink()
#   
#   # find corresponding wx station
#   met_site <- substr(wq_site, 1, 3)
#   met_site <- grep(paste0('^', met_site, '.*met'), files_s3, value = T)
#   met_site <- gsub('\\.RData$', '', met_site)
# 
#   # continue if wx data found
#   if(length(met_site) > 0){
#     
#     # if > 1 wx site, pick the one with more obs
#     if(length(met_site) > 1){
# 
#       met_list <- vector('list', length(met_site))
#       names(met_list) <- met_site
#       for(met in met_site){
#       
#         met_tmp <- import_remote(met)
#         met_list[[met]] <- met_tmp
#       
#       }
#     
#       # pick the one with most obs
#       met_most <- which.max(unlist(lapply(met_list, nrow)))
#       met <- met_list[met_most][[1]]
# 
#     # otherwise load only one
#     } else {
#     
#       # met
#       met <- import_remote(met_site)
#     
#     }
#     
#     ##
#     # load the wq file
#     
#     # wq
#     wq <- import_remote(wq_site)
#     
#     ## 
#     # combine, estimate metabolism, reduce data volume
#     dat <- comb(wq, met, method = attr(met, 'station'))
#     dat <- ecometab(dat)
#     dat <- dat[1, ]
#     
#     dat
#     
#   }
#   
# }
# names(metabs) <- wq_sites
# save(metabs, file = 'metabs.RData')

# # take all metab estimates and summarize by year
# # done for two stations at each reserve with the longest time series
# data(metabs)
# 
# metabs <- lapply(metabs, attr, 'metabolism')
# metabs <- do.call('rbind', metabs)
# metabs$site <- gsub('\\.[0-9]*$', '', as.character(row.names(metabs)))
# row.names(metabs) <- 1:nrow(metabs)
# 
# library(dplyr)
# library(tidyr)
# metabs <- select(metabs, date, Pg, Rt, NEM, site) %>% 
#   mutate(date = as.numeric(strftime(date, '%Y'))) %>% 
#   gather('metab', 'value', 2:4) %>% 
#   group_by(date, site, metab) %>% 
#   summarize(value = mean(value, na.rm = T)) %>% 
#   group_by(site, metab) %>% 
#   na.omit %>% 
#   mutate(reserve = substr(site, 1, 3)) %>% 
#   spread(metab, value)
# 
# # select two sites from each reserve, those with longest records
# metabs <- split(metabs, metabs$reserve)
# metabs <- lapply(metabs, 
#   function(x){
#     
#     num_yrs <- aggregate(date ~ site, x, length)
#     num_yrs <- num_yrs[order(num_yrs$date, decreasing = T), ]
#     
#     if(nrow(num_yrs) >1){
#       site_sel <- num_yrs$site[c(1, 2)]
#     } else {
#       site_sel <- num_yrs$site[1]
#     }
#     
#     out <- x[x$site %in% site_sel, ]
#     return(out)
#     
#   }
#   
# )
# metabs <- do.call('rbind', metabs)
# 
# metabs_sum <- metabs
# save(metabs_sum, file = 'data/metabs_sum.RData')

data(metabs_sum)

library(dplyr)
library(tidyr)

# summarize for annual means, get conf ints
metabs_plo <- gather(metabs_sum, 'metab', 'value', 4:6) %>% 
  group_by(site, metab) %>% 
  summarize(
    margs = qt(1 - 0.05/2, length(value) - 1) * sd(value)/sqrt(length(value)),
    value = mean(value)
    ) %>% 
  mutate(
    value = 0.032 * value,
    margs = 0.032 * margs,
    upper = value + margs, 
    lower = value - margs
    )

# plot prep
to_plo <- data.frame(metabs_plo)

#reassign factors for ranking in plot
sort_val <- order(to_plo[to_plo$metab == 'Pg', 'value'])
to_plo$site <- factor(gsub('wq$', '', to_plo$site))
to_plo$site <- factor(
  to_plo$site,
  levels = levels(to_plo$site)[sort_val],
  labels = levels(to_plo$site)[sort_val]
  )
new_labs <- c('Mean net annual metabolism', 'Mean annual gross production', 'Mean annual total respiration')
to_plo$metab <- factor(to_plo$metab, levels = c('NEM', 'Pg', 'Rt'), labels = new_labs)

ylabs <- expression(paste('g ', O[2],' ', m^-2,' ', d^-1))
p <- ggplot(to_plo, 
    aes(x = site, y = value, group = metab, fill = metab)
  ) + 
  geom_bar(stat = 'identity', width = 1, colour = 'black') + 
  scale_y_continuous(ylabs) + 
  facet_wrap( ~ metab, ncol = 1, scales = 'free_y') + 
  scale_x_discrete(name = element_blank()) + 
  theme_classic() + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, 
      size = 8),
    legend.position = 'none'
    ) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0)
print(p)

% table summary of trends
<<eval = F, cache = T, echo = F>>=

data(metabs_sum)

library(dplyr)
library(tidyr)

# summarize for annual means, get conf ints
metabs_tab <- gather(metabs_sum, 'metab', 'value', 4:6)
metabs_tab$yr_grp <- '1995 - 2004'
metabs_tab$yr_grp[metabs_tab$year > 2004] <- '2005-2014'
metabs_tab <- mutate(metabs_tab, value = 0.032 * value) %>% 
  group_by(metabs_tab, site, metab, yr_grp)

# summarize trends

@@

@@

Quickly access all \ac{SWMP} data from 1995 through 2014. See the help file for \texttt{import\_remote} for more information: \href{https://s3.amazonaws.com/swmpalldata/}{https://s3.amazonaws.com/swmpalldata/}

### 2015-03-24 swmpr_manu.tex
processed all new cdmo data for metabolism, added plot

First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at the \ac{NERRS} reserve for all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update to results described in Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04}.   The results are presented to facilitate additional research to evaluate factors that influence variation between sites.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} describe the theory and application of the open-water method to estimate ecosystem metabolism using two sites at each of the \ac{NERRS} reserve.  Time series data included approximately five years of half-hour water quality observations at each site.  Additionally, the air-sea gas exchange model, as implemented by the current \texttt{ecometab} function (see Ro and Hunt \cite{Ro06} and Thebault et al. \cite{Thebault08}), was not incorporated into the initial metabolism estimates such that a constant value for the reaeration coefficient was assumed.  This coefficient provides an estimate of the rate of air-sea gas exchange that varies as a function of wind speed, temperature, barometric pressure, salinity, and depth of the water column  The inclusion of weather data in the calculation allows for a more precise estimate of air-sea gas exchange and consequently more reliable estimates of ecosystem metabolism (see Caffrey et al. \cite{Caffrey14} for details).

All water quality and weather observations for all \ac{NERRS} sites were obtained through a bulk data request in November 2014 using the \href{http://cdmo.baruch.sc.edu/aqs/zips.cfm}{zip downloads} feature of \ac{CDMO}.  After the download was complete, all csv files for each station were imported into R using the \texttt{import\_local} function, saved again on a local hard drive as a binary .RData file, and uploaded.  This resulted in a single \texttt{swmpr} object for each site.  All files were then uploaded to a remote server.  An \href{https://gist.github.com/fawda123/4fc51c2cb86341ed9291}{R script} was executed that retrieved and processed combined water quality and weather data for each site.

>>>>

First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at the \ac{NERRS} reserve for all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update to results described in Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} using the most recent \ac{SWMP} data.  Additionally, previous methods to evaluate metabolism at \ac{NERRS} reserves did not incorporate \textit{in situ} weather data to estimate the air-sea gas exchange model.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} applied the open-water method to estimate ecosystem metabolism using five years of water quality observations at two sites at each of the \ac{NERRS} reserves.  Additionally, the air-sea gas exchange model assumed a constant value for the reaeratio coefficientt.  This coefficient provides an estimate of the rate of air-sea gas exchange that varies as a function of wind speed, temperature, barometric pressure, salinity, and depth of the water column.  The inclusion of weather data in the calculation allows for a more precise estimate of air-sea gas exchange and consequently more reliable estimates of ecosystem metabolism (see Caffrey et al. \cite{Caffrey14} for details).

Water quality and weather observations from January 1995 to December 2014 for all \ac{NERRS} sites were obtained through a bulk data request using the \href{http://cdmo.baruch.sc.edu/aqs/zips.cfm}{zip downloads} feature of \ac{CDMO}.  After the download was complete, all csv files for each station were imported into R using the \texttt{import\_local} function, processed using the \texttt{setstep} and \texttt{qaqc} functions, then saved on a local hard drive as binary RData files (see \href{https://github.com/fawda123/swmp_rats/blob/master/R/dat_proc.R}{here} for the R script). This resulted in a single \texttt{swmpr} object for each paramter at each site.  All files were then uploaded to a remote server.  An \href{https://gist.github.com/fawda123/4fc51c2cb86341ed9291}{R script} was executed that retrieved and processed combined the water quality and weather data for each site.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figure/metab_plo}

\caption[Aggregated estimates of net metabolism, gross production, and total respiration for two sites at each \ac{NERRS} reserve]{Aggregated estimates of net metabolism, gross production, and total respiration for two sites at each \ac{NERRS} reserve.  Values are daily integrated estimates as mean annual values averaged across all years with 95\% confidence intervals.  Two sites were chosen from each reserve that had the longest available time series.\label{fig:metab_plo}}
\end{figure}

% table summary of trends
